MT @HanBaldwin: Fightin OOVs in German \#twitter

### 2013-08-01 darmstadt_gscl_2013/article_twitter_normalization.tex
small update

Here once again the question of classification arose. This time with
regard to the reasons, why different tokens could have been omitted
from corresponding applications' dictionaries. In this respect,
division into following groups seemed to be appropriate for us:
\begin{enumerate}
  \item \textbf{Objective limitedness of machine-readable dictionary
    (MRD)}. To this group we counted words of basic vocabulary which
    did not get into applications' MRD either because they supposedly
    were rare or because they did not exist at the time when
    dictionaries were created. Another reason for the inclusion in
    this type was the belonging of a word to an open lexical or
    part-of-speech class (like, for example, named entities or
    interjections) which are often omitted from MRDs due to
    impossibility to fully cover these classes;\label{dict}
  \item \textbf{Unintended sloppiness of users' input}. In the scope
    of this second group, we considered unintended typos including
    unexpected truncation of words at the end of Twitter
    messages\footnote{As is generally known, Twitter imposes a strong
      restriction on the length of posted messages which can be no
      longer than 140 characters. Upon exceeding this length, tweets
      get automatically truncated to maximal allowed
      length.};\label{spell}
  \item \textbf{Stylistic specifics of text genre}. This group
    comprised words which could be considered as illegal from the
    point of view of standard language texts but were perfectly valid
    terms in the domain of web discourse and Twitter communication in
    particular.\label{style}
\end{enumerate}

@@

As it is clear from the table, deletions are by far the most common
type of spelling mistakes. This results on the one hand from
deliberate or unintended omissions of characters made by users but an
even more common source of these ill-formed words is automatic
truncation of messages made by Twitter.

>>>>

Here once again the question of classification arose. This time with
regard to the reasons, why different tokens could have been omitted
from corresponding applications' dictionaries. In this respect,
division into following groups seemed to be appropriate for us:
\begin{enumerate}
  \item \textbf{Objective limitedness of machine-readable dictionary
    (MRD)}. To this group we counted words of basic vocabulary which
    did not get into applications' MRD either because they supposedly
    were rare or because they did not exist at the time when
    dictionaries were created. Another reason for the inclusion in
    this type was the belonging of a word to an open lexical or
    part-of-speech class (like, for example, named entities or
    interjections) which are often omitted from MRDs due to
    impossibility to fully cover these classes;\label{dict}
  \item \textbf{Unintended sloppiness of users' input}. In the scope
    of this second group, we considered unintended typos;\label{spell}
  \item \textbf{Stylistic specifics of text genre}. This group
    comprised words which could be considered as illegal from the
    point of view of standard language texts but were perfectly valid
    terms in the domain of web discourse and Twitter communication in
    particular.\label{style}
\end{enumerate}

@@

As it is clear from the table, deletions are by far the most common
type of spelling mistakes. This results on the one hand from
deliberate or unintended omissions of characters made by users but an
even more common source of these ill-formed words was automatic
truncation of words at the end of tweets made by Twitter service
itself. \footnote{As is generally known, Twitter imposes a strong
  restriction on the length of posted messages which can be no longer
  than 140 characters. Upon exceeding this length, tweets get
  automatically truncated to maximal allowed length.}
